---
title: "Vaccine in Indonesia"
author: "Felicia Haliman"
date: "4/3/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read Data `Vaccine`

# Embed `library`
```{r}
library(glue)
library(ggrepel)
library(ggridges)
library(ggthemes)
library(leaflet)
library(lubridate)
library(scales)
library(tidyverse)
library(sf)
library(rnaturalearth)
library(padr)
library(plotly)
library(magick)
```

```{r}
vaccine <- read.csv("data_input/country_vaccinations.csv")
head(vaccine)
```
## Clean Data

```{r}
colSums(is.na(vaccine))
```
```{r}
vaccine_clean <- vaccine %>% 
  drop_na(total_vaccinations,people_vaccinated,people_fully_vaccinated,daily_vaccinations_raw,daily_vaccinations,total_vaccinations_per_hundred,people_fully_vaccinated_per_hundred,people_fully_vaccinated_per_hundred,daily_vaccinations_per_million)
```

```{r}
colSums(is.na(vaccine_clean))
```

# Clean!

# 1.Actually i just interest how many ppl vaccinated in Indonesia

```{r}
vaccine_indonesia <- vaccine_clean[vaccine_clean$country == "Indonesia", ]
vaccine_indonesia
```



## Check the data `boxplot`

```{r}
boxplot(vaccine_indonesia$people_vaccinated)
```

# 2.normal

## Start make the visualization

```{r}
aggregate(people_vaccinated ~ country, vaccine_indonesia, sum)
```

# 3.total `12348556` ppl vaccinated


```{r}
ggplot(vaccine_indonesia, aes(x = people_vaccinated,
                        y = total_vaccinations,
                        size = people_vaccinated,
                        color = country)
       ) +
  geom_point() +
  scale_color_manual(values = c("red", "blue", "green"))
```

# 4.`insight`: between total vaccine and ppl vaccinated balance

`Conclusion:`
1.Actually i just interested with how many ppl vaccinated in Indonesia\
2.normal\
3.total `12348556` vaccinated\
4.`insight`: between total vaccine and ppl vaccinated balance


```{r}
# Based on data, 12348556 ppl vaccinated and government great to handle
```
